Depression and suicidality as costly signals of need

### 2021-04-12 Paper.rmd

```{r socioeconomic, fig.width=8, fig.cap="Distribution of participants by age, log income (USD), and nationality. A small number of participants who did not report income, or reported values < $10 USD, were removed from this plot. A small amount of jitter was added to reveal overlapping points."}

@@

d %>% 
  dplyr::filter(!is.na(Age), !is.na(Income), Income >= 10) %>% 
  mutate(
    Nationality = ifelse(sample == 'American', 'US', 'India'),
    logIncome = log10(Income)
  ) %>% 
  ggplot(aes(Age, logIncome, colour = Nationality)) +
  geom_jitter(width = 0.5, alpha = 0.35) +
  geom_hline(yintercept = log10(1670), linetype = 'dotted', colour = clrs[1]) +
  geom_hline(yintercept = log10(35977), linetype = 'dotted', colour = clrs[2]) +
  annotate('text', 15, log10(35977), label = 'Median US income', hjust = 1) +
  annotate('text', 15, log10(1670), label = 'Median India income', hjust = 1) +
  scale_color_binary() +
  guides(colour = guide_legend(reverse = T, override.aes = list(alpha=1))) +
  coord_cartesian(clip = 'off') +
  labs(x = '\nAge (years)', y = 'Log annual\nincome (USD)') +
  theme_minimal(15) +
  theme(axis.title.y = element_text(angle = 0, hjust=0))

>>>>

```{r socioeconomic, fig.width=8, fig.cap="Distribution of participants by age, log annual income (USD), and nationality. Each dot is one participant. A small number of participants who did not report annual income, or reported values < $10 USD, were removed from this plot. A small amount of jitter was added to reveal overlapping points."}

@@

d %>% 
  dplyr::filter(!is.na(Age), !is.na(Income), Income >= 10) %>% 
  mutate(
    Nationality = ifelse(sample == 'American', 'US', 'India'),
    logIncome = log10(Income)
  ) %>% 
  ggplot(aes(Age, logIncome, colour = Nationality)) +
  geom_jitter(width = 0.5, alpha = 0.35) +
  geom_hline(yintercept = log10(2266), linetype = 'dotted', colour = clrs[1]) +
  geom_hline(yintercept = log10(68703), linetype = 'dotted', colour = clrs[2]) +
  annotate('text', 85, log10(68703), label = 'Median US\nincome', hjust = 0) +
  annotate('text', 85, log10(2266), label = 'Median India\nincome', hjust = 0) +
  scale_color_binary() +
  guides(colour = guide_legend(reverse = T, override.aes = list(alpha=1, size = 3))) +
  coord_cartesian(clip = 'off') +
  labs(x = '\nAge (years)', y = 'Log annual\nincome (USD)') +
  theme_minimal(15) +
  theme(
    plot.margin = unit(c(1,5,1,1), "lines"),
    axis.title.y = element_text(angle = 0, hjust=0), 
    legend.position = 'top'
    )
